Spotify Data

### 2024-10-10 paper/paper.qmd
Updated Authors

---
title: "Spotify Data"
author: "Yanzun Jiang, "
date: today
date-format: long
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "Spotify Data"
author: "Yanzun Jiang, Siyuan Lu, Yi Tang, Jin Zhang"
date: today
date-format: long
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
